The pollination trade-off

### 2018-12-09 paper/manuscript.Rmd
Spellcheck discussion

Our results suggest that the community context plays a central role at determining competition for pollination. 
First, we found that the costs of pollinator sharing are pervasive. In particular, we found that a significant proportion of species undergoes overall neutral or competitive effects from animal mediated pollination. 
Second, we found that plants are able to minimise the intensity of this competition using multiple strategies, however, conspecific and heterospecific pollen deposition are tightly coupled and threfore these strategies are likely to involve a trade-off between the quantity and quality of pollination. 
Third, we found that these strategies are strongly shaped by the community context, this is, the same plant species can adopt dramatically different strategies depending on the comminity it belongs to.

\R{disc-facil-comp}Both of the tests we used to identify the effect of animal-mediated pollination suggested the same outcome: that overall facilitation is only experienced by a minority of species in a community. 
Althouh a recent study already suggested a wide range of outcomes in multi-species context [@tur_evaluating_2016], the factors determining why some species experience more competition than others were not understood. 
Here we show that prevalence of neutral and competitive effects of animal-mediated pollination can be, at least partially, explained by the trade-offs that minimising competition involves.

These trade-offs were most evident precisely in the strategies that most strongly modulate pollen deposition. 
We found that the strategies that increased the relative dominance of the species (in terms of pollen and visits, or abundance) also tended to be the most important predictors of pollen deposition. 
Adopting a strategy of high visitation increasses the rates of conspecific pollen deposition at the expense of a reduction in the quality of pollination even when the visitors carry a high proportion of conspecific pollen. 
Similarly, adopting a strategy of high abundance reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen. 
Our results corroborate the importance that previous studies have attributed to the role that visitation and abundance play at determining competition for pollination [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008]. 
The fact that they also involve a trade-off between the quantity and quality of pollination might explain the often contrasting results that these studies, based on two or three species systems obtained.

Simultaneously, because visitation, pollen production and abundance are correlated [@sargent_role_2006], the trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between increassing conspecific pollen and reduce heterospecific pollen deposition. 
The relative wide range of coefficients in our models might be explained by the large variation of the extent to which plant species are affected by pollen deposition. 
While some plant species experience a large reduction on seed set due to heterospecific pollen deposition, some others are relatively insensitive to heterospecific pollen but are greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].

The two other strategies we analysed involved a smaller trade-off than the abundance or visit efficacy. 
Specifically, having high functional originality relative to other species in the community or sharing few pollinators was found to be benetitial to both the quantity and quality of pollination.
Interestingly, these two strategies also had lower explanatory power in the models of pollen deposition. 
This does not necessarily implies that these variables are unimportant to pollen deposition. 
Instead, it is possible that the processes that underlay these strategies might be more complex than what our metrics are able to capture. 
Particularly so for conspecific pollen deposition, which was harder to predict than heterospecific pollen. 
For instance, having distinct traits, for example through phenology differentiation, might have a positive impact on the pollination service only to the extent to which previous floral communities have promoted high pollinator densities (ref). 
In addition, some plants have been shown possess mechanisms that prevent heterospecific pollen deposition even when shared visitors carry pollen loads from diverse species. 
Alternatively, other factors that we were unable to meassure, like pollinator behaviour and densities [@ye_competition_2014; @flanagan_effects_2011; @melissas_2019?] or the spatial context [@cariveau_spatially_2009], can also shape the way sharing pollinators affect the pollination service.

>>>>

Our results suggest that the community context plays a central role in determining competition for pollination. 
First, we found that the costs of pollinator sharing are pervasive. In particular, we found that a significant proportion of species undergoes overall neutral or competitive effects from animal-mediated pollination. 
Second, we found that plants are able to minimise the intensity of this competition using multiple strategies, however, conspecific and heterospecific pollen deposition are tightly coupled and therefore these strategies are likely to involve a trade-off between the quantity and quality of pollination. 
Third, we found that these strategies are strongly shaped by the community context, this is, the same plant species can adopt dramatically different strategies depending on the community it belongs to.

\R{disc-facil-comp}Both of the tests we used to identify the effect of animal-mediated pollination suggested the same outcome: that overall facilitation is only experienced by a minority of species in a community. 
Although a recent study already suggested a wide range of outcomes in a multi-species context [@tur_evaluating_2016], the factors determining why some species experience more competition than others were not understood. 
Here we show that the prevalence of neutral and competitive effects of animal-mediated pollination can be, at least partially, explained by the trade-offs that minimising competition involves.

These trade-offs were most evident precisely in the strategies that most strongly modulate pollen deposition. 
We found that the strategies that increased the relative dominance of the species (in terms of pollen and visits, or abundance) also tended to be the most important predictors of pollen deposition. 
Adopting a strategy of high visitation increases the rates of conspecific pollen deposition at the expense of a reduction in the quality of pollination even when the visitors carry a high proportion of conspecific pollen. 
Similarly, adopting a strategy of high abundance reduces the amount of heterospecific pollen deposited but at the expense of a noticeable reduction in the amount of conspecific pollen. 
Our results corroborate the importance that previous studies have attributed to the role that visitation and abundance play at determining competition for pollination [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008]. 
The fact that they also involve a trade-off between the quantity and quality of pollination might explain the often contrasting results that these studies, based on two or three species systems obtained.

Simultaneously, because visitation, pollen production and abundance are correlated [@sargent_role_2006], the trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between increasing conspecific pollen and reduce heterospecific pollen deposition. 
The relatively wide range of coefficients in our models might be explained by the large variation of the extent to which plant species are affected by pollen deposition. 
While some plant species experience a large reduction on seed set due to heterospecific pollen deposition, some others are relatively insensitive to heterospecific pollen but are greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985].

The two other strategies we analysed involved a smaller trade-off than the abundance or visit efficacy. 
Specifically, having high functional originality relative to other species in the community or sharing few pollinators was found to be beneficial to both the quantity and quality of pollination.
Interestingly, these two strategies also had lower explanatory power in the models of pollen deposition. 
This does not necessarily imply that these variables are unimportant to pollen deposition. 
Instead, it is possible that the processes that underlay these strategies might be more complex than what our metrics are able to capture. 
Particularly so for conspecific pollen deposition, which was harder to predict than heterospecific pollen. 
For instance, having distinct traits, for example through phenology differentiation, might have a positive impact on the pollination service only to the extent to which previous floral communities have promoted high pollinator densities (ref). 
In addition, some plants have been shown possess mechanisms that prevent heterospecific pollen deposition even when shared visitors carry pollen loads from diverse species. 
Alternatively, other factors that we were unable to measure, like pollinator behaviour and densities [@ye_competition_2014; @flanagan_effects_2011; @melissas_2019?] or the spatial context [@cariveau_spatially_2009], can also shape the way sharing pollinators affect the pollination service.
